RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R

### 2014-06-24 manuscripts/manuscript.Rmd
clarified that 'content' is the name of an attribute, not the text data that is subtended by the focal DOM node
clarified that CURIE prefixes are not the same as XML namespace prefixes

We see the title appears as the `content` of this `meta` element.
The `id` attribute provides us with a unique way to refer to this meta
element in this document.  The `datatype` tells us that the content
is a text string (as opposed to, say, a numerical or boolean value).
The `property` is the attribute that most interests us here; it tells us
that the content is a title.  The prefix `dc` indicates the vocabulary
(called a namespace in XML) to which the word `title` belongs.  The prefix
is defined elsewhere in the NeXML file, as we can see with:

>>>>

We see the title appears as the value of the `content` attribute of this `meta` element.
The `id` attribute provides us with a unique way to refer to this meta
element in this document.  The `datatype` tells us that the content
is a text string (as opposed to, say, a numerical or boolean value).
The `property` is the attribute that most interests us here; it tells us
that the content is a title.  The prefix `dc` indicates the vocabulary
(here identified as an XML namespace) to which the word `title` belongs.  The prefix
is defined elsewhere in the NeXML file, as we can see with:
